---
title: "Euclidean distance and its projection"
author: "Andrea Sánchez Tapia"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r remedy}
setwd("~/Documents/1 ModelR/package docs/4 tests euclidean")

```

```{r}
library(rJava)
library(raster)
#library(ModelR)
devtools::load_all("../../ModelR")
library(dplyr)
```

# Dataset

```{r}
especies <- unique(coordenadas$sp)
coord1sp <- dplyr::filter(coordenadas, sp == especies[1])
head(coord1sp)
dim(coord1sp)
ceiling(0.7 * nrow(coord1sp))
set <- sample(1:nrow(coord1sp), size = ceiling(0.7 * nrow(coord1sp)))
train_set <- coord1sp[set,]
test_set <- coord1sp[setdiff(1:nrow(coord1sp),set),]

```

# Fitting and projection datasets

We want to fit everything in a small area around the occurrence points (generated through a "median distance buffer") and project it to other sample rasterStacks 

A simple model with no buffer and no projection: 

```{r enm1, message = F, eval = F}
fit_data <- stack("./env/cropped_proj.tif")
no_proj <- do_enm(species_name = especies[1],
                 occurrences = coord1sp[, -1],
                 predictors = fit_data,
                 models_dir = "./fit",
                 centroid = T,
                 mindist = T,
                 clean_dupl = T,
                 clean_nas = T)

no_proj.c <- raster("./fit/Eugenia florida DC./present/partitions/centroid_cont_Eugenia florida DC._1_1.tif")
#no_proj.m <- raster("./fit/Eugenia florida DC./present/partitions/mindist_cont_Eugenia florida DC._1_1.tif")
par(mfrow = c(1,2))
plot(no_proj.c, main = "centroid")
maps::map(, , add = T)
plot(no_proj.m, main = "mindist")
maps::map(, , add = T)
```

## New implementation


```{r remedy001}
fit_data <- stack("/Users/Sanchez/Documents/1 ModelR/package docs/2 projection/env/cropped_proj.tif")
source("/Users/Sanchez/Documents/1 ModelR/ModelR/R/euclidean.R")

no_proj <- do_any2(species_name = especies[1],
                 occurrences = coord1sp[, -1],
                 predictors = fit_data,
                 models_dir = "./eucl_test",
                 algo = "centroid",
                 #centroid = T,
                 clean_dupl = T,
                 clean_nas = T)
no_proj.test <- raster("./eucl_test/Eugenia florida DC./present/partitions/centroid_cont_Eugenia florida DC._1_1.tif")
plot(no_proj.test)
#identical(no_proj.test, no_proj.c)
par(mfrow = c(1,2))
plot(no_proj.test)
#plot(no_proj.c)
no_proj.test
#no_proj.c
```

##mindist
```{r remedy002}

no_proj <- do_any2(species_name = especies[1],
                 occurrences = coord1sp[, -1],
                 predictors = fit_data,
                 models_dir = "./eucl_test",
                 algo = "mindist",
                 clean_dupl = T,
                 clean_na = T)
no_proj.test2 <- raster("./eucl_test/Eugenia florida DC./present/partitions/mindist_cont_Eugenia florida DC._1_1.tif")
plot(no_proj.test2)
par(mfrow = c(1,2))
plot(no_proj.test2)
no_proj.test2
```

## Model projection

We project to a series of projections in the specified folder: "./env/proj"

```{r proj, message = T, eval = F}
yes_proj <- do_any2(species_name = especies[1],
                    occurrences = coord1sp[, -1],
                    predictors = fit_data,
                    models_dir = "./projtest",
                    algo = "centroid",
                    #algo = "mindist",
                    clean_dupl = T,
                    clean_nas = T,
                    project_model = T,
                    proj_data_folder = "./env/proj",
                    write_png = T,
                    )
```
