---
title: "Projecting models"
author: "Andrea Sánchez Tapia"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```
    
```{r}
library(rJava)
library(raster)
#library(ModelR)
devtools::load_all("../../ModelR")
library(dplyr)
```

# Dataset

```{r}
especies <- unique(coordenadas$sp)
coord1sp <- dplyr::filter(coordenadas, sp == especies[1])
head(coord1sp)
dim(coord1sp)
ceiling(0.7 * nrow(coord1sp))
set <- sample(1:nrow(coord1sp), size = ceiling(0.7 * nrow(coord1sp)))
train_set <- coord1sp[set,]
test_set <- coord1sp[setdiff(1:nrow(coord1sp),set),]

```

# Fitting and projection datasets

We want to fit everything in a small area around the occurrence points (generated through a "median distance buffer") and project it to other sample rasterStacks 

```{r, fig.height = 6}
fit_data <- stack("./env/cropped_proj.tif")
proj_folder <- "./env/proj/proj1/"
proj_data <- list.files(proj_folder, full.names = T) %>% stack() %>% .[[1]]
pts <- SpatialPoints(coord1sp[,c(2,3)])

    plot(!is.na(example_vars[[1]]), legend = F, add = F)
plot(fit_data[[1]], legend = F, add = T)
plot(proj_data[[1]], legend = F, add = T)
#points(train_set[,2:3], col = "red", pch = 19)
#points(test_set[,2:3], col = "blue", pch = 19)

```


## Model projection

A simple model with no buffer and no projection: 

```{r enm1, message = F, eval=F}
no_proj <- do_enm(species_name = especies[1],
                 occurrences = coord1sp[, -1],
                 predictors = fit_data,
                 models_dir = "./fit",
                 bioclim = T,
                 svm.k = T,
                 clean_dupl = T,
                 clean_na = T)

no_proj.bc <- raster("./fit/Eugenia florida DC./present/partitions/bioclim_cut_Eugenia florida DC._1_1.tif")
no_proj.svmk <- raster("./fit/Eugenia florida DC./present/partitions/svm.k_cut_Eugenia florida DC._1_1.tif")
plot(no_proj.bc)
maps::map(, , add = T)
plot(no_proj.svmk)
maps::map(, , add = T)
```


We project to a series of projections in the specified folder: "./env/proj"

```{r proj, message = F, eval = T}
yes_proj <- do_enm(species_name = especies[1],
                 occurrences = coord1sp[, -1],
                 predictors = fit_data,
                 models_dir = "./projtest",
                 bioclim = T,
                 domain = T, 
                 glm = T,
                 mahal = T,
                 maxent = T,
                 rf = T,
                 svm.k = T,
                 svm.e = T,
                 brt = T,
                 clean_dupl = T,
                 clean_na = T,
                 project_model = T,
                 proj_data_folder = "./env/proj",
                 write_png = T)
```

```{r list_results}
no_proj.bc <- raster("./projtest/Eugenia florida DC./present/partitions/bioclim_cont_Eugenia florida DC._1_1.tif")
no_proj.svmk <- raster("./projtest/Eugenia florida DC./present/partitions/svm.k_cont_Eugenia florida DC._1_1.tif")
yes_proj1.bc <- raster("./projtest/Eugenia florida DC./proj1/partitions/bioclim_cont_Eugenia florida DC._1_1.tif")
yes_proj1.svmk <- raster("./projtest/Eugenia florida DC./proj1/partitions/svm.k_cont_Eugenia florida DC._1_1.tif")
yes_proj2.svmk <- raster("./projtest/Eugenia florida DC./proj2/partitions/svm.k_cont_Eugenia florida DC._1_1.tif")
yes_proj2.bc <- raster("./projtest/Eugenia florida DC./proj2/partitions/bioclim_cont_Eugenia florida DC._1_1.tif")
yes_proj3 <- raster("./projtest/Eugenia florida DC./proj3/partitions/svm.k_cont_Eugenia florida DC._1_1.tif")
yes_proj4 <- raster("./projtest/Eugenia florida DC./proj4/partitions/svm.k_cont_Eugenia florida DC._1_1.tif")
plot(no_proj.bc, main = "no proj bioclim")
maps::map(,,add = T)
plot(no_proj.svmk, main = "no proj svm.k")
maps::map(,,add = T)
plot(yes_proj1.bc, main = "proj1 bioclim")
maps::map(,,add = T)
plot(yes_proj1.svmk, main = "proj1 svm.k")
maps::map(,,add = T)
plot(yes_proj2.bc, main = "proj2 bioclim")
maps::map(,,add = T)
plot(yes_proj2.svmk, main = "proj2 svmk")
maps::map(,,add = T)
plot(yes_proj3)
maps::map(,,add = T)
plot(yes_proj4)
maps::map(,,add = T)
```

# Final model projection


The `final_model` function has a parameter `proj_dir` that allows it to be run using any projection. 
We can project the models fit to the present 

```{r remedy001}
args(final_model)
final_model(species_name = especies[1],
            models_dir = "./projtest")
```

or the projected models, 
```{r remedy002}
args(final_model)
final_model(species_name = especies[1],
            models_dir = "./projtest",
            proj_dir = "proj1")
final_model(species_name = especies[1],
            models_dir = "./projtest",
            proj_dir = "proj2")
final_model(species_name = especies[1],
            models_dir = "./projtest",
            proj_dir = "proj3")
final_model(species_name = especies[1],
            models_dir = "./projtest",
            proj_dir = "proj4")
```
