---
title: "Projecting models"
author: "Andrea Sánchez Tapia"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

Here we test the function `setup_sdmdata()` and its different parametrization options. This function prepares the data to run the models with `do_any()` or `do_many()` functions. It creates an object in the workspace to be used in `do_any()` or `do_many()` and writes two csv files with metadata and sdmdata.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = TRUE, cache = FALSE)
```

Loading required packages.

```{r load}
library(rJava)
library(raster)
library(dplyr)
library(maps)
library(maptools)

```

```{r load_all, echo = FALSE, eval = TRUE}
#eu estou usando uma cópia local para desenvolvimento
devtools::load_all("../../1_modleR/")
#devtools::load_all("../1_modleR/")
```

# Selecting one species as an example

We use a standard dataset inside the package `modleR`. First, from `example_occs` object we select only data from one species *Abarema langsdorffii* and create one training set (70% of the data) and one test set (30% of the data) for the data.

```{r dataset}
## Creating an object with species names
especies <- names(example_occs)[1]
# Selecting only coordinates for the first species
coord1sp <- example_occs[[1]]
head(coord1sp)
dim(coord1sp)
# Subsetting data into training and test
ceiling(0.7 * nrow(coord1sp))
# Making a sample of 70% of species' records
set <- sample(1:nrow(coord1sp), size = ceiling(0.7 * nrow(coord1sp)))
# Creating training data set (70% of species' records)
train_set <- coord1sp[set,]
# Creating test data set (other 30%)
test_set <- coord1sp[setdiff(1:nrow(coord1sp),set),]
```

Now lets the check our data points. We plot the traning and test data sets with the first axis of the environmental PCA data from the object `example_vars`.

```{r plotdataset}
# selecting only the first PCA axis
predictor <- example_vars[[1]]
# transforming the data frame with the coordinates in a spatial object
pts <- SpatialPoints(coord1sp[,c(2,3)])
# ploting environmental layer
plot(predictor, legend = FALSE)
points(lat ~ lon, data=coord1sp)
```


# Fitting and projection datasets

We want to fit everything in a small area around the occurrence points (generated through a "median distance buffer") and project it to other sample rasterStacks 

```{r, fig.height = 6}
fit_data <- stack("../data/env/cropped_proj.tif")
proj_folder <- "../data/env/proj/proj1/"
proj_data <- list.files(proj_folder, full.names = TRUE) %>%
    stack() %>%
    .[[1]]
pts <- SpatialPoints(coord1sp[,c(2,3)])

plot(!is.na(example_vars[[1]]), legend = FALSE, add = FALSE)
plot(fit_data[[1]], legend = FALSE, add = TRUE)
plot(proj_data[[1]], legend = FALSE, add = TRUE)
points(train_set[,2:3], col = "red", pch = 19)
points(test_set[,2:3], col = "blue", pch = 19)

```


## Model projection

A simple model with no buffer and no projection: 

```{r enm1, message = FALSE, eval = TRUE}
# generating sdmdata
sdm_no_proj <- setup_sdmdata(species_name = especies[1], 
                             occurrences = coord1sp[,-1],
                             predictors=fit_data, 
                             models_dir="projection/fit", 
                             clean_dupl = TRUE, 
                             clean_na = TRUE)
# running models
no_proj <- do_many(species_name = especies[1],
                 predictors = fit_data,
                 models_dir = "projection/fit",
                 bioclim = TRUE,
                 svmk = TRUE)

no_proj.bc <- raster("projection/fit/Abarema_langsdorffii/present/partitions/bioclim_cont_Abarema_langsdorffii_1_1.tif")
no_proj.svmk <- raster("projection/fit/Abarema_langsdorffii/present/partitions/svmk_cont_Abarema_langsdorffii_1_1.tif")
plot(no_proj.bc)
maps::map(, , add = TRUE)
plot(no_proj.svmk)
maps::map(, , add = TRUE)
```


We project to a series of projections in the specified folder: `"./env/proj"`

```{r proj, message = FALSE, eval = TRUE}
## first renaming layer names from predictors to match proj files 
names(fit_data) <- paste0("proj1_", 1:6)

sdm_yes_proj <- setup_sdmdata(species_name = especies[1],
                              occurrences = coord1sp[, -1],
                              predictors = fit_data,
                              models_dir = "projection/projtest",
                              clean_dupl = TRUE,
                              clean_na = TRUE,
                              buffer_type = "median",
                              partition_type = "bootstrap",
                              boot_n = 3)

yes_proj1 <- modleR::do_any(species_name = especies[1],
                 predictors = fit_data,
                 models_dir = "projection/projtest",
                 algo = "bioclim",
                 project_model = TRUE,
                 proj_data_folder = "data/env/proj/",
                 png_partitions = TRUE)

yes_proj <- do_many(species_name = especies[1],
                    predictors = fit_data,
                    models_dir = "projection/projtest",
                    bioclim = TRUE,
                    domain = TRUE,
                    glm = TRUE,
                    mahal = FALSE,
                    maxent = TRUE,
                    rf = TRUE,
                    svmk = TRUE,
                    svme = TRUE,
                    brt = TRUE,
                    project_model = TRUE,
                    proj_data_folder = "../data/env/proj/",
                    png_partitions = TRUE)
```

```{r list_results}
results <- list.files("projection/projtest", pattern = ".tif$", recursive = TRUE, full.names = TRUE)
length(results)#oito algoritmos, 5 projeções (present e as demais, nem vou plotar)
```

# Final model projection


The `final_model()` function has a parameter `proj_dir` that allows it to be run using any projection. We can project the models fit to the present.

```{r remedy001, eval = TRUE}
args(final_model)

final_model_present <- final_model(species_name = especies[1],
                                   models_dir = "projection/projtest",
                                   select_par = "TSSmax",
                                   select_par_val = 0,
                                   proj_dir = "present", 
                                   overwrite = TRUE)
```

or the projected models, 

```{r remedy002, eval = TRUE}
final_model_proj1 <- final_model(species_name = especies[1],
                                 models_dir = "projection/projtest",
                                 select_par = "TSSmax",
                                 select_par_val = 0,
                                 proj_dir = "proj1", overwrite = TRUE)

final_model_proj2 <- final_model(species_name = especies[1],
            models_dir = "projection/projtest",
            select_par = "TSSmax",
            select_par_val = 0,
            proj_dir = "proj2", overwrite = TRUE)

final_model_proj3 <- final_model(species_name = especies[1],
            models_dir = "projection/projtest",
            select_par = "TSSmax",
            select_par_val = 0,
            proj_dir = "proj3", overwrite = TRUE)

final_model_proj4 <- final_model(species_name = especies[1],
            models_dir = "projection/projtest",
            select_par = "TSSmax",
            select_par_val = 0,
            proj_dir = "proj4", overwrite = TRUE)
```

